\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-15 papers/jss/article.Rnw
Comment out additional redundant information to make section 3 a more concise introduction.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@899 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<echo=FALSE,print=FALSE>>=
ls("RProtoBuf:DescriptorPool")
@

% \subsection{Creating a message}
\textbf{Creating, accessing, and modifying a message.}

@@

%\subsection{Display messages}
\textbf{Printing, Reading, and Writing Messages}

@@

For additional information, such as for debugging purposes,
the \code{as.character} method provides a more complete ASCII
representation of the contents of a message.

@@

The same method can be used to serialize messages to files:

@@

Or to arbitrary binary connections:

<<>>=
tf2 <- tempfile()
con <- file(tf2, open = "wb")
serialize(p, con)
close(con)
readBin(tf2, raw(0), 500)
@

@@

The \code{input} argument of \code{read} can also be a binary
readable \proglang{R} connection, such as a binary file connection:

<<>>=
con <- file(tf2, open = "rb")
message <- read(tutorial.Person, con)
close(con)
writeLines(as.character(message))
@

Finally, the raw vector payload of the message can be used:

<<>>=
payload <- readBin(tf1, raw(0), 5000)
message <- read(tutorial.Person, payload)
@

>>>>

%<<echo=FALSE,print=FALSE>>=
%ls("RProtoBuf:DescriptorPool")
%@

% \subsection{Creating a message}

\\

\textbf{Creating, accessing, and modifying messages.}

@@

%\subsection{Display messages}

\\

\textbf{Printing, Reading, and Writing Messages}

@@

%For additional information, such as for debugging purposes,
The \code{as.character} method provides a more complete ASCII
representation of the contents of a message.

@@

The same method can be used to serialize messages to files or arbitrary binary connections:

@@

% TODO(mstokely): Comment out, combined with last statement. make this
% shorter, more succinct summary of the key features of RProtoBuf.

%Or to arbitrary binary connections:
%
%<<>>=
%tf2 <- tempfile()
%con <- file(tf2, open = "wb")
%serialize(p, con)
%close(con)
%readBin(tf2, raw(0), 500)
%@

@@

The \code{input} argument of \code{read} can also be a binary
readable \proglang{R} connection, such as a binary file connection, or a raw vector of serialized bytes.

% <<>>=
% con <- file(tf2, open = "rb")
% message <- read(tutorial.Person, con)
% close(con)
% writeLines(as.character(message))
% @

% Finally, the raw vector payload of the message can be used:
%
%<<>>=
%payload <- readBin(tf1, raw(0), 5000)
%message <- read(tutorial.Person, payload)
%@
